Using SMT engine to generate Symbolic Automata\thanks{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai}

### 2018-01-16 2017-Xudong-SMT/FM-2018-extended.tex

%\usepackage{amsfonts}
%\usepackage{fancyhdr}
%\usepackage{cite}
%\usepackage{ifthen}
%\usepackage{amssymb}
%\usepackage{fancyhdr}
%\usepackage{pifont}
\usepackage{stmaryrd}
\usepackage{mathtools,mathpartir}
\usepackage{proof}
%\usepackage{setspace}
%\usepackage{indentfirst}
\usepackage{amsmath,amssymb,amscd,mathrsfs}
% \usepackage{array,booktabs,arydshln,xcolor}
\usepackage{array,booktabs,xcolor}
\DeclareGraphicsRule{.tif}{png}{.png}{`convert #1 `dirname #1`/`basename #1 .tif`.png}
\usepackage{epsfig,color,subfigure,enumitem}
\newcommand{\TODO}[1]{\textcolor{red}{\textbf{[TODO:#1]}}}
\newcommand{\NOTE}[1]{\textcolor{blue}{\textbf{[NOTE:#1]}}}
\newcommand{\ERIC}[1]{\textcolor{blue}{#1}}
\newcommand{\OTvar}{\texttt}
\newcommand{\OTland}{\;\land\ }
\definecolor{airforceblue}{rgb}{0.26, 0.44, 0.56}
\newcommand{\QIN}[1]{\textcolor{airforceblue}{#1}}
\newcommand{\coloncolon}{{:\hspace{-.2ex}:}}
\makeatletter
\newcommand{\raisemath}[1]{\mathpalette{\raisem@th{#1}}}
\newcommand{\raisem@th}[3]{\raisebox{#1}{$#2#3$}}
\makeatother

@@

 %% \begin{figure}[t]
 %%   \centerline{\includegraphics[width=12cm]{XFIG/BIPspec-ArchFailureTimerMax}}
 %%   \caption{FailureTimer Architecture in BIP graphical syntax}  \label{schema:BIParchitecture}
 %% \end{figure}

\begin{figure}[t]
   \centerline{\includegraphics[width=12cm]{XFIG/FailureTimerPNET}}
   \caption{FailureTimer pNet encoding\TODO{on peut gagner un peu en hauteur}}  \label{schema:BIParchitecture}
 \end{figure}

@@

% \newpage
\appendix

>>>>

%\usepackage{amsfonts}
%\usepackage{fancyhdr}
%\usepackage{cite}
%\usepackage{ifthen}
%\usepackage{amssymb}
%\usepackage{fancyhdr}
%\usepackage{pifont}
\usepackage{stmaryrd}
\usepackage{mathtools,mathpartir}
\usepackage{proof}
%\usepackage{setspace}
%\usepackage{indentfirst}
\usepackage{amsmath,amssymb,amscd,mathrsfs}
% \usepackage{array,booktabs,arydshln,xcolor}
\usepackage{array,booktabs,xcolor}
\DeclareGraphicsRule{.tif}{png}{.png}{`convert #1 `dirname #1`/`basename #1 .tif`.png}
\usepackage{epsfig,color,enumitem}
\usepackage[%
    font={small,sf},
    labelfont=bf,
    format=hang,    
    format=plain,
    margin=0pt,
    width=0.8\textwidth,
]{caption}
\usepackage[list=true]{subcaption}

\newcommand{\TODO}[1]{\textcolor{red}{\textbf{[TODO:#1]}}}
\newcommand{\NOTE}[1]{\textcolor{blue}{\textbf{[NOTE:#1]}}}
\newcommand{\ERIC}[1]{\textcolor{blue}{#1}}
\newcommand{\OTvar}{\texttt}
\newcommand{\OTland}{\;\land\ }
\definecolor{airforceblue}{rgb}{0.26, 0.44, 0.56}
\newcommand{\QIN}[1]{\textcolor{airforceblue}{#1}}
\newcommand{\coloncolon}{{:\hspace{-.2ex}:}}
\makeatletter
\newcommand{\raisemath}[1]{\mathpalette{\raisem@th{#1}}}
\newcommand{\raisem@th}[3]{\raisebox{#1}{$#2#3$}}
\makeatother

@@

 \begin{figure}[t]
   \centering
   \includegraphics[width=\columnwidth]{XFIG/BIPspec-ArchFailureTimerMax-v2}
   \caption{The BIP specification of the FailureTimer architecture}
   \label{schema:ArchFailure:BIP}
 \end{figure}
%
   %% \hfill
%
 \begin{figure}[t]
   \centering
   \includegraphics[width=\columnwidth]{XFIG/FailureTimerPNET}
   \caption{pNet encoding of the FailureTimer architecture}
   \label{schema:ArchFailure:pNet}
 \end{figure}

@@

% \newpage
%\appendix
